### 2023-05-17 resilience-safe-down.tex
sections

@@

\begin{proof}
Downward compatibility of $\mathscr{S}=(S,\rightarrow, \leq)$ 
means that
for all $s_1, s_2, t_1 \in S$ with
$s_2 \leq s_1$ and $s_1 \to t_1$
there
exists $t_2 \in S$ with
$t_2 \leq t_1$ and $s_2 \to^* t_2$.

>>>>

Let us recall that a system $\mathscr{S}=(S,\rightarrow, \leq)$ is downward compatible if
for all $s_1, s_2, t_1 \in S$ with
$s_2 \leq s_1$ and $s_1 \to t_1$
there
exists $t_2 \in S$ with
$t_2 \leq t_1$ and $s_2 \to^* t_2$.

@@

\begin{proof}
